Reading Notes

### 2020-07-15 reading-notes.tex
chores done for today--learned that martini isn't as cool as I thought for new molecules!!

\cite{Cao2015a}

>>>>

\cite{Cao2015a}
if the properties you are interested in a electrostatic, then a CG mapping operator based on centers of charge in the molecule should be best.
mapping operators are chosen based on desired resolution and the information to be extracted. straightforward way is to group three or four heavy atoms together. In the MARTINI force field four types of atoms are grouped and the bead is classified as polar, non-polar, apolar, or charged. 
use chemical intuition--e.g. what parts of the molecule shouldn't be allowed to bend?
